Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-18 paper.tex
fixed special char bug
Summary of Nextflow

        All configuration options can be set/changed by modifying the
\textit{cfg\_<type>} files.

@@

        \subsection{limitations of SPM}
    \section{Nexflow}
        \subsection{summary}
    \section{OpenMOLE}
        \subsection{summary} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}

>>>>

        All configuration options can be set/changed by modifying the
\textit{cfg\_$\langle type \rangle$ } files.

@@

        \subsection{limitations of SPM}
    \section{Nextflow}
        \subsection{summary}
        Nextflow is a POSIX-compatible pipeline engine for scientific workflows.
It extends the Groovy programming language to provide an  intuitive domain-specific language (DSL) 
that enables users to easily describe their workflows. Unlike pipeline engines such as Nipype and
PSOM, Netflow does not employ DAG. It instead adheres to the
\textit{Dataflow} programming model which decides how data will flow through the pipeline at
runtime \note{fix this sentence}. Nextflow prides itself on allowing the
integration of containerized tools to address the issue of numerical stability
that may arise from different environment setups.

        \note{Pipeline description}
        A Nextflow pipeline is represented by the flow of data between processes. These
processes can be written in any Linux-compatible scripting language. As in Nipype, 
these processes are executed in an isolated environment. The only means
of communication between processes is through asynchronous FIFO queues known as
\textit{channels}. Each process can contain any number of input and output
channels. Through the use of channels, input and output can be stored not only
on disk but also in-memory \note{Nipype can also return outputs that are not on
disk, so this is nothing special}.

        As with other pipeline engines (nipype, psom, etc.,), the order in which
the processes appear is irrelevant. Execution order is determined by the dependencies.

        \note{Pipeline execution}
        The \textit{executor} is responsible for the execution of a Nextflow
pipeline. By default, it assumes that the pipeline is to be run locally. The
local executor will use multithreading in order to exploit available cores
within the local environment. To configure the executor to run in a remote distributed environment, it is
necessary to modify the configuration file to specify the environment. By
following this approach, Nextflow users can seamlessly run their code on various
processing platforms with a simple modification to a configuration file. In
addition to local, Nextflow currently has executors for SGE, LSF, SLURM,
PBS/Torque, NQSII, HTCondor, DRMAA, Ignite, Kubernetes and AWS Batch.

        \note{Debugging and Provenance}
        When executing a pipeline, it is always possible to specify the
generation of a execution report. The report is written in HTML and consists of three sections:
Summary, Resources and Tasks. Summary provides details on the execution command,
execution status, overall execution time, in addtion to other metadata. The
Resources tab, on the other hand, contains several HighChart plots representing
CPU, memory, time and disk read/write rate of each pipeline process. The final
section, Tasks, contains many metrics including the status and command script of
each task.

    Other reports that can be generated at runtime include the Trace report and
the Timeline report. The Trace report include details such as CPU usage, start
time, submission time, etc, of each process that was executed, whereas, the
Timeline report generates an HTML timeline of all processes that have been
executed.

    \note{doesn't seem to be anything on provenance...}

    \section{FastR}
        \subsection{summary}
        \note{Pipeline description}
        \note{Pipeline execution}
        \note{Debugging and Provenance}
    \section{OpenMOLE}
        \subsection{summary}
        \note{Pipeline description}
        \note{Pipeline execution}
        \note{Debugging and Provenance}
    \section{LONI}
    \section{Automatic Analysis}
    \section{Dipy, Make, Pydiper} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}
